### 2021-02-25 manuscript/manuscript-speed-accuracy.tex
Added limitations discussion to manuscript, fixed figures, removed highlighting of values.

We found that software speed, author reputation, journal impact, the
number of citations and age are all unreliable predictors of software
accuracy. This is unfortunate because citations, author and journal
reputation are frequently used reasons for selecting software
tools. Our results do show that accurate bioinformatic software tools
are generally the product of many gradual improvements, often from
multiple developers, based upon matching GitHub records with benchmark results. 
In addition, we find
that the field of bioinformatics has an excess of slow and inaccurate software
tools, this is consistent across many sub-disciplines. Meanwhile, there are few tools that
are middle-of-road in terms of accuracy and speed trade-offs. We
hypothesise that a form of publication-bias unduly influences the
publication and development of bioinformatic software. In other
words, software that is intermediate in terms of both speed and accuracy may be difficult to publish due to author,
editor and reviewer practices. This leaves an unfortunate gap in the
literature as the ideal tools may fall in the gap e.g. high accuracy is generally not useful if years of CPU time is required, 
while high speed is not useful if the results are very inaccurate.  }

@@

For common computational biology tasks, a proliferation of
software-based solutions often exists
\cite{Felsenstein1995-ic,Altschul2013-bv,Henry2014-ut,Wikipedia_contributors2015-vj,Wikipedia_contributors2015-hr}. While
this is a good problem to have, and points to a
diversity of options from which practical solutions can be selected,
having many possible options creates a dilemma for users. In the absence of
any recent gold-standard benchmarks, how should scientific software be
selected? In the following we presume that ``biological
accuracy'' is the most desirable feature for a software tool. Biological
accuracy is the degree to which predictions or measurements reflect
the biological truths based on expert-derived curated datasets (see Methods for the  mathematical definition used here). In some
fields biological accuracy is very difficult to ascertain, for
example, in phylogenetics it is nearly impossible in most cases to know the
true ancestral relationships between organisms. In situations like this,
researchers may use simulated or high-confidence datasets.

@@

With the wide adoption of GitHub ($\approx 47\%$ of the
\textbf{{\color{red}\numTools}} tools included in this study could be
linked to a GitHub repository), quantifiable data on software
development such as the number of contributors to code, number of code
changes and versions is also available
\cite{ray2014large,Dozmorov:2018,mangul2018comprehensive}.

In the following study, we explore factors that may be indicative of
software accuracy. This, in our opinion, should be one of the prime
reasons for selecting a software tool. We have mined the large and
freely accessible PubMed database \cite{Sayers2010-vm} for benchmarks
of computational biology software, and manually extracted accuracy and
speed rankings for \textbf{{\color{red}\numTools~}} unique software tools. For
each tool, we have collected measures that may be predictive
of accuracy, and may be subjectively employed by the research
community as a proxy for software quality. These include relative
speed, relative age, the productivity and impact of the corresponding
authors, journal impact and the number of citations.

\section*{Results}
We have collected relative accuracy and speed ranks for
\textbf{{\color{red}\numTools~}} distinct software tools. This software has
been developed for solving broad cross-section computational biology
tasks.
Each software tool was benchmarked in at least one of
\textbf{{\color{red}\numBenchmarkPubs~}} publications that satisfy the Boulesteix
criteria \cite{Boulesteix2013-vb}. In brief, the Boulesteix criteria
are: 1. the main focus of the article is a benchmark. 2. the authors
are reasonably neutral. 3. the test data and evaluation criteria are
sensible.

@@

\begin{figure*}[ht]
\includegraphics[width=\textwidth]{figure1.pdf}
\caption{\textbf{A.} A heatmap indicating the relationships between
  proposed predictors of software quality. Spearman’s rho is used to
  infer correlations between metrics such as the H- and M-indices of
  corresponding authors, number of citations, journal impact factors
  and H5 indices, the year and relative age of software and the mean
  relative rankings of software speed and accuracy. Red colours
  indicate a positive correlation, blue colours indicate a negative
  correlation. Correlations with an uncorrected P-value less than 0.05 are
  indicated with a `$\vartimes$'. The dashed rectangular area is illustrated in
  more detail in \textbf{B}, the relationship between speed and
  accuracy is shown in more detail in \textbf{Figure 2}.
  %The
  %dendrogram was computed using the default ‘heatmap.2 function in R,
  %which computes a Euclidean distance matrix and a complete-linkage
  %hierarchical clustering.
  \textbf{B.} A barplot illustrating the correlation, as measured by
  Spearman’s rho, between normalised accuracy ranks and software tool
  features that may be predictive of accuracy. In order to give an
  appreciation of the difference between the observed effect-sizes and
  significant effect sizes, we generated 1000 permuted accuracy ranks
  for each benchmark and recorded Spearman’s rho for the significant
  correlations with an uncorrected P-value less than 0.05.
  These values are marked with blues `$\vartimes$'s in the
  barplot. Significant correlations are marked with red asterisks.}
\label{fig:allfactors}
\end{figure*}

Data on the
number of updates to software tools from GitHub such as the number of versions,
commits and contributors \textbf{{\color{red}was significantly correlated with 
accuracy (respective Spearman’s rhos = 0.13, 0.22, 0.21, respective uncorrected P-values = 0.0027, 0.00079, 0.0013). 
These features were not correlated with speed however (see Figure~\ref{fig:allfactors}A).
}}
We also found that author reputation metrics, journal impacts and the age
of tools were generally \textbf{not} correlated with either tool
accuracy or speed (see Figure~\ref{fig:allfactors}). The strongest
association was between accuracy and \textbf{{\color{red}the relative
    number of citations}} (Spearman’s rho = \textbf{{\color{red}0.092,
    P-value = 0.047}}). But the effect size is only just over the
significance threshold and may be explained by multiple-testing.

@@

In order to gain a deeper understanding of the distribution of
available bioinformatic software tools on a speed versus accuracy
landscape, we ran a permutation test. The ranks extracted
from each benchmark were randomly permuted, generating 1,000
randomized speed and accuracy ranks. In the cells of a $10\times10$
grid spanning the normalised speed and accuracy ranks we computed a
Z-score for the observed number of tools in a cell, compared to the
expected distributions generated by 1,000 randomized ranks. The results
of this are shown in Figure~\ref{fig:speedaccuracy}. We identified \textbf{{\color{red}18}}
bins where there was a significant excess or dearth of tools. For
example, there was an excess of “slow and inaccurate” software (\textbf{{\color{red}Z=2.50,
P-value=0.0063}}). We find that the amount of software classed as “fast
and accurate”, “fast and inaccurate” and "slow and accurate" are at approximately the
expected proportions based upon the permutation test. 
While there are very few tools placed in the middle of the ranks on accuracy and speed.
The number of
significant results is in excess, and is not due to multiple testing, as
the probability of finding \textbf{{\color{red}18}} of 100 tests significant by chance is
low (P-value = \textbf{{\color{red}$2.2\times 10^{-6}$}}, exact binomial test).

@@

\begin{figure*}[ht]
%\includegraphics[scale=0.55]{figure2.pdf}
\centering
\includegraphics[width=0.75\textwidth]{figure2.pdf}
\caption{A heatmap indicating the relative paucity or abundance of
  software in the range of possible accuracy and speed rankings. Red
  colours indicate an abundance of software tools in an accuracy and
  speed category, while blue colours indicate scarcity of software in
  an accuracy and speed category. The abundance is quantified using a
  Z-score computation for each bin, this is derived from 10,000 random
  permutations of the speed and accuracy ranks from each
  benchmark. Mean normalised ranks of accuracy and speed have been
  binned into 100 classes (a $10\times10$ grid) that range from
  comparatively slow/inaccurate to comparatively
  fast/accurate. Z-scores with a P-value less than 0.05 are indicated
  with a ‘$\vartimes$’.}
\label{fig:speedaccuracy}
\end{figure*}

There is a major reduction in the number of software tools that are
classed as intermediate in terms of both speed and accuracy based on
permutation tests (see Methods for details, Figure~\ref{fig:speedaccuracy}). The cells
corresponding to the four central deciles are
highlighted \textbf{{\color{red}(Z = -1.9, -2.5, -2.9 and -1.1, P-values = 0.03, 0.006,
0.002 and 0.14}}, respectively, reading from top to bottom, left to
right). We also tested the relative age of the software tools in
the indicated corners and central regions of the speed vs
accuracy plot. We found that the “slow and inaccurate” tools ($N=27$) were
generally published earlier than ``fast and accurate'' tools ($N=23$) \textbf{{\color{red}(W = 341, P=0.005,
one-tailed Wilcoxon test)}} (Figure S7).

@@

We have gathered data on the relative speeds and accuracies of
\textbf{{\color{red}\numTools~}} bioinformatic tools from
\textbf{{\color{red}\numBenchmarkPubs}} benchmarks published between
2005 and 2020. {\bf Our results suggest there are major benefits for
  long term support for software \cite{siepel2019challenges}.} The
finding of a strong relationship between the number of commits to
GitHub (i.e. software updates) and accuracy, highlights the benefits of
long-term development.

@@

We found the lack of a correlation between software speed and accuracy
surprising.  The slower software tools are overrepresented at both
high and low levels of accuracy (Figure~\ref{fig:speedaccuracy}).
In addition, we find an under-representation of software that has
intermediate levels of both accuracy and speed. A possible explanation
for this is that bioinformatic software tools are bound by a form of
publication-bias \cite{Boulesteix2015-am,Nissen:2016}. That is, the
probability that a study being published is influenced by the results
it contains \cite{sterling1995publication}. The community of
developers, reviewers and editors may be unwilling to publish software
that is not highly ranked on speed or accuracy. If correct, this may
have unfortunate consequences.  We also found that slow and inaccurate
software is generally published earlier than fast and accurate tools
\textbf{{\color{red}(P=0.007, one-tailed Wilcoxon test)}}, therefore
comparisons were not required to publish the slow and
inaccurate tools.

@@

{\bf DESCRIBE STUDY LIMITATIONS... 
\begin{itemize}
    \item Difficult to test publication biases
    \item Heterogeneous measures of accuracy between benchmarks  
    \item possible lack of independence between different benchmarks 
    \item Non-uniform inclusion of tools in different benchmarks -- some tools ranked many times (e.g. velvet and soap assemblers ranked 26 different times)
    \item How to deal with inconsistently reported versioning of software? 
    \item Metrics and tools performance are all moving targets, only a snap shot is used here  
\end{itemize}
}

We propose that the full spectrum of software tool accuracies and
speeds serve a useful purpose to the research community. Like negative
results, if honestly reported, illustrate to the research community
that certain approaches are not practical research avenues
\cite{Ioannidis2005-xh,Workman1999-au,Rivas2000-fb}.
The current
practices of publishers, editors, reviewers and authors of software
tools therefore deprive our community of tools for building effective
and productive workflows.

The most reliable way to select software tools is through neutral
software benchmarks \cite{Boulesteix2013-vb}. We are hopeful that
this, along with steps to reduce the publication-bias we have
described, will reduce the over-optimistic and misleading reporting of
tool accuracy \cite{Boulesteix2010-te,Jelizarow2010-zf,Norel2011-cq}.

@@

For stage 2, in order to compute a log-odds score for bioinformatic
words, we computed the frequency of words that were not removed by our
high frequency filter in two different groups of articles:
bioinformatics-background and bioinformatics-benchmark articles. The
text from bioinformatics-background articles were drawn from the
bioinformatics literature, but these were not necessarily associated
with benchmark studies. For background text we used Pubmed
(\cite{Sayers2010-vm,McEntyre2001-fl} to select 8,908 articles that
contained the word “bioinformatics” in the title or abstract and were
published between 2013 and 2015. We computed frequencies for each word
by combining text from titles and abstracts for the background and
training articles. A log-odds score is computed for each word using
the following formula:
%\todo{Word is denoted $w$ on the left and $word$ on the right.}
$lo(word)=\log_2\frac{f_{tr}(word)+\delta}{f_{bg}(word)+\delta}$, where
$\delta$
is a prior probability ($\delta = 10^{-5}$, by default),
$f_{bg}(word)$ and $f_{tr}(word)$ are the frequencies of a $word$ in
the background and training datasets respectively. Word frequencies
are computed by counting the number of times a word appears in the
pool of titles and abstracts, the counts are normalised by the total
number of words in each set.

@@

A score is computed for each candidate article by summing the log-odds
scores for the words in title and abstract,
i.e. $s(a)=\sum_i^Nlo(w_i)$. The high scoring candidate articles are
then manually evaluated against the ALB-criteria. Accuracy and speed
ranks are extracted from the articles that meet the criteria, and
these are also added to the set of training articles. The evaluated
candidate articles that do not meet the ALB-criteria are incorporated
into the set of background articles. This process is iterated and has resulted in the identification of
\textbf{{\color{red}\numBenchmarkPubs}} benchmark articles, that
contain \textbf{{\color{red}\numBenchmarks}} different benchmarks, together these
rank \textbf{{\color{red}\numTools~}} distinct software packages.

@@

\section*{Data availability}
Raw datasets, software and documents are available under a CC-BY license:\\
\fussy
\url{https://docs.google.com/spreadsheets/d/14xIY2PHNvxmV9MQLpbzSfFkuy1RlzDHbBOCZLJKcGu8/edit?usp=sharing}\\
and here:\\
\fussy
\url{https://dx.doi.org/10.6084/m9.figshare.4299320.v1}\\
\sloppy
Additional documentation, code, figures and raw data is available here:\\
\fussy
\url{https://github.com/Gardner-BinfLab/speed-vs-accuracy-meta-analysis}
\sloppy

@@

{\bf AND ETC....}

>>>>

We found that software speed, author reputation, journal impact, the
number of citations and age are all unreliable predictors of software
accuracy. This is unfortunate because citations, author and journal
reputation are frequently used reasons for selecting software
tools. Our results do show that accurate bioinformatic software tools
are generally the product of many gradual improvements, often from
multiple developers, based upon matching GitHub records with benchmark results. 
In addition, we find
that the field of bioinformatics has an excess of slow and inaccurate software
tools, this is consistent across many sub-disciplines. Meanwhile, there are few tools that
are middle-of-road in terms of accuracy and speed trade-offs. We
hypothesise that a form of publication-bias unduly influences the
publication and development of bioinformatic software. In other
words, software that is intermediate in terms of both speed and accuracy may be difficult to publish due to author,
editor and reviewer practices. This leaves an unfortunate gap in the
literature as the ideal tools may fall in the gap e.g. high accuracy tools are not always useful if years of CPU time are required, 
while high speed is not useful if the results are also inaccurate.  }

@@

For common computational biology tasks, a proliferation of
software-based solutions often exists
\cite{Felsenstein1995-ic,Altschul2013-bv,Henry2014-ut}. While
this is a good problem to have, and points to a
diversity of options from which practical solutions can be selected,
having many possible options creates a dilemma for users. In the absence of
any recent gold-standard benchmarks, how should scientific software be
selected? In the following we presume that ``biological
accuracy'' is the most desirable feature for a software tool. Biological
accuracy is the degree to which predictions or measurements reflect
the biological truths based on expert-derived curated datasets (see Methods for the  mathematical definition used here). In some
fields biological accuracy is very difficult to ascertain, for
example, in phylogenetics it is nearly impossible in most cases to know the
true ancestral relationships between organisms. In situations like this,
researchers may use simulated or high-confidence datasets.

@@

With the wide adoption of GitHub ($\approx 47\%$ of the
{\color{black}\numTools} tools included in this study could be
linked to a GitHub repository), and consequently quantifiable data on software
development such as the number of contributors to code, number of code
changes and versions is also available
\cite{ray2014large,Dozmorov:2018,mangul2018comprehensive}.

In the following study, we explore factors that may be indicative of
software accuracy. This, in our opinion, should be one of the prime
reasons for selecting a software tool. We have mined the large and
freely accessible PubMed database \cite{Sayers2010-vm} for benchmarks
of computational biology software, and manually extracted accuracy and
speed rankings for {\color{black}\numTools~} unique software tools. For
each tool, we have collected measures that may be predictive
of accuracy, and may be subjectively employed by the research
community as a proxy for software quality. These include relative
speed, relative age, the productivity and impact of the corresponding
authors, journal impact and the number of citations.

\section*{Results}
We have collected relative accuracy and speed ranks for
{\color{black}\numTools~} distinct software tools. This software has
been developed for solving broad cross-section computational biology
tasks.
Each software tool was benchmarked in at least one of
{\color{black}\numBenchmarkPubs~} publications that satisfy the Boulesteix
criteria \cite{Boulesteix2013-vb}. In brief, the Boulesteix criteria
are: 1. the main focus of the article is a benchmark. 2. the authors
are reasonably neutral. 3. the test data and evaluation criteria are
sensible.

\begin{figure*}[htb!]
\includegraphics[width=\textwidth]{figure1.pdf}
\caption{\textbf{A.} A heatmap indicating the relationships between
  proposed predictors of software quality. Spearman’s rho is used to
  infer correlations between metrics such as the H- and M-indices of
  corresponding authors, number of citations, journal impact factors
  and H5 indices, the year and relative age of software and the mean
  relative rankings of software speed and accuracy. Red colours
  indicate a positive correlation, blue colours indicate a negative
  correlation. Correlations with an uncorrected P-value less than 0.05 are
  indicated with a `$\vartimes$'. The dashed rectangular area is illustrated in
  more detail in \textbf{B}, the relationship between speed and
  accuracy is shown in more detail in \textbf{Figure 2}.
  %The
  %dendrogram was computed using the default ‘heatmap.2 function in R,
  %which computes a Euclidean distance matrix and a complete-linkage
  %hierarchical clustering.
  \textbf{B.} A barplot illustrating the correlation, as measured by
  Spearman’s rho, between normalised accuracy ranks and software tool
  features that may be predictive of accuracy. In order to give an
  appreciation of the difference between the observed effect-sizes and
  significant effect sizes, we generated 1000 permuted accuracy ranks
  for each benchmark and recorded Spearman’s rho for the significant
  correlations with an uncorrected P-value less than 0.05.
  These values are marked with blues `$\vartimes$'s in the
  barplot. Significant correlations are marked with red asterisks.}
\label{fig:allfactors}
\end{figure*}

@@

Data on the
number of updates to software tools from GitHub such as the number of versions,
commits and contributors was significantly correlated with 
accuracy (respective Spearman’s rhos = {\color{black}0.13, 0.22, 0.21,} respective uncorrected P-values = {\color{black}0.0027, 0.00079, 0.0013}). 
These features were not correlated with speed however (see Figure~\ref{fig:allfactors}A).
We also found that author reputation metrics, journal impacts and the age
of tools were generally \textbf{not} correlated with either tool
accuracy or speed (see Figure~\ref{fig:allfactors}). The strongest
association was between accuracy and the relative
number of citations (Spearman’s rho = {\color{black}0.092,
P-value = 0.047}). But the effect size is only just over the
significance threshold and may be the result of multiple-testing.

@@

In order to gain a deeper understanding of the distribution of
available bioinformatic software tools on a speed versus accuracy
landscape, we ran a permutation test. The ranks extracted
from each benchmark were randomly permuted, generating 1,000
randomized speed and accuracy ranks. In the cells of a $10\times10$
grid spanning the normalised speed and accuracy ranks we computed a
Z-score for the observed number of tools in a cell, compared to the
expected distributions generated by 1,000 randomized ranks. The results
of this are shown in Figure~\ref{fig:speedaccuracy}. We identified {\color{black}18}
bins where there was a significant excess or dearth of tools. For
example, there was an excess of “slow and inaccurate” software ({\color{black}Z=2.50,
P-value=0.0063}). We find that the amount of software classed as “fast
and accurate”, “fast and inaccurate” and "slow and accurate" are at approximately the
expected proportions based upon the permutation test. 
While there are very few tools placed in the middle of the ranks on accuracy and speed.
The number of
significant results is in excess, and is not due to multiple testing, as
the probability of finding {\color{black}18} of 100 tests significant by chance is
low (P-value = {\color{black}$2.2\times 10^{-6}$}, exact binomial test).

@@

\begin{figure*}[htb!]
%\includegraphics[scale=0.55]{figure2.pdf}
\centering
\includegraphics[width=0.75\textwidth]{figure2.pdf}
\caption{A heatmap indicating the relative paucity or abundance of
  software in the range of possible accuracy and speed rankings. Red
  colours indicate an abundance of software tools in an accuracy and
  speed category, while blue colours indicate scarcity of software in
  an accuracy and speed category. The abundance is quantified using a
  Z-score computation for each bin, this is derived from 10,000 random
  permutations of the speed and accuracy ranks from each
  benchmark. Mean normalised ranks of accuracy and speed have been
  binned into 100 classes (a $10\times10$ grid) that range from
  comparatively slow/inaccurate to comparatively
  fast/accurate. Z-scores with a P-value less than 0.05 are indicated
  with a ‘$\vartimes$’.}
\label{fig:speedaccuracy}
\end{figure*}

There is a major reduction in the number of software tools that are
classed as intermediate in terms of both speed and accuracy based on
permutation tests (see Methods for details, Figure~\ref{fig:speedaccuracy}). The cells
corresponding to the four central deciles are
highlighted {\color{black}(Z = -1.9, -2.5, -2.9 and -1.1, P-values = 0.03, 0.006,
0.002 and 0.14}, respectively, reading from top to bottom, left to
right). We also tested the relative age of the software tools in
the indicated corners and central regions of the speed vs
accuracy plot. We found that the “slow and inaccurate” tools ($N=27$) were
generally published earlier than ``fast and accurate'' tools ($N=23$) {\color{black}(W = 341, P=0.005,
one-tailed Wilcoxon test)} (Figure S7).

@@

We have gathered data on the relative speeds and accuracies of
{\color{black}\numTools~} bioinformatic tools from
{\color{black}\numBenchmarkPubs} benchmarks published between
2005 and 2020. Our results provide significant support for the suggestion that there are major benefits to
the long-term support of software development \cite{siepel2019challenges}. The
finding of a strong relationship between the number of commits and code contributors to
GitHub (i.e. software updates) and accuracy, highlights the benefits of
long-term development.

@@

We found the lack of a correlation between software speed and accuracy
surprising.  The slower software tools are overrepresented at both
high and low levels of accuracy (Figure~\ref{fig:speedaccuracy}).
In addition, we find an under-representation of software that has
intermediate levels of both accuracy and speed. A possible explanation
for this is that bioinformatic software tools are bound by a form of
publication-bias \cite{Boulesteix2015-am,Nissen:2016}. That is, the
probability that a study being published is influenced by the results
it contains \cite{sterling1995publication}. The community of
developers, reviewers and editors may be unwilling to publish software
that is not highly ranked on speed or accuracy. If correct, this may
have unfortunate consequences.  We also found that slow and inaccurate
software is generally published earlier than fast and accurate tools
{\color{black}(P=0.007, one-tailed Wilcoxon test)}, therefore
comparisons were not required to publish the slow and
inaccurate tools.

@@

While we have taken pains to mitigate many issues with our analysis, nevertheless 
some limitations remain. For example, it has proven difficult to verify if the gap in medium accuracy 
and medium speed software is genuinely the result of publication bias, or due to additional factors that we have 
not taken in to account. In addition, all of the features we have used here are moving targets, e.g. as software 
tools are refined, their relative accuracies and speeds will change, the citation metrics, ages, and version control 
derived measures also change over time. We merely report a snapshot of values from 2020.  The benchmarks themselves may 
also introduce biases into the study, for example there are issues with a potential lack of independence between benchmarks 
(e.g. shared datasets, metrics and tools), there are heterogeneous measures of accuracy and speed and often unclear 
processes for including different tools.

%{\bf DESCRIBE STUDY LIMITATIONS... 
%\begin{itemize}
%    \item Difficult to test publication biases
%    \item Heterogeneous measures of accuracy between benchmarks  
%    \item possible lack of independence between different benchmarks 
%    \item Non-uniform inclusion of tools in different benchmarks -- some tools ranked many times (e.g. velvet and soap assemblers ranked 26 different times)
%    \item How to deal with inconsistently reported versioning of software? 
%    \item Metrics and tools performance are all moving targets, only a snap shot is used here  
%\end{itemize}
%}

We propose that the full spectrum of software tool accuracies and
speeds serve a useful purpose to the research community. Like negative
results, if honestly reported, illustrate to the research community
that certain approaches are not practical research avenues
\cite{fanelli2012negative}. % Ioannidis2005-xh,Workman1999-au,Rivas2000-fb}.
The current
practices of publishers, editors, reviewers and authors of software
tools therefore may be depriving our community of tools for building effective
and productive workflows.

The most reliable way to identify accurate software tools is through neutral
software benchmarks \cite{Boulesteix2013-vb}. We are hopeful that
this, along with steps to reduce the publication-bias we have
described, will reduce the over-optimistic and misleading reporting of
tool accuracy \cite{Boulesteix2010-te,Jelizarow2010-zf,Norel2011-cq}.

@@

For stage 2, in order to compute a log-odds score for bioinformatic
words, we computed the frequency of words that were not removed by our
high frequency filter in two different groups of articles:
bioinformatics-background and bioinformatics-benchmark articles. The
text from bioinformatics-background articles were drawn from the
bioinformatics literature, but these were not necessarily associated
with benchmark studies. For background text we used Pubmed
(\cite{Sayers2010-vm,McEntyre2001-fl} to select 8,908 articles that
contained the word “bioinformatics” in the title or abstract and were
published between 2013 and 2015. We computed frequencies for each word
by combining text from titles and abstracts for the background and
training articles. A log-odds score is computed for each word using
the following formula:
%\todo{Word is denoted $w$ on the left and $word$ on the right.}
$lo(word)=\log_2\frac{f_{tr}(word)+\delta}{f_{bg}(word)+\delta}$, where
$\delta$
is a pseudo-count added for each word ($\delta = 10^{-5}$, by default),
$f_{bg}(word)$ and $f_{tr}(word)$ are the frequencies of a $word$ in
the background and training datasets respectively. Word frequencies
are computed by counting the number of times a word appears in the
pool of titles and abstracts, the counts are normalised by the total
number of words in each set.

@@

A score is computed for each candidate article by summing the log-odds
scores for the words in title and abstract,
i.e. $s(a)=\sum_i^Nlo(w_i)$. The high scoring candidate articles are
then manually evaluated against the ALB-criteria. Accuracy and speed
ranks are extracted from the articles that meet the criteria, and
these are also added to the set of training articles. The evaluated
candidate articles that do not meet the ALB-criteria are incorporated
into the set of background articles. This process is iterated and has resulted in the identification of
{\color{black}\numBenchmarkPubs} benchmark articles, that
contain {\color{black}\numBenchmarks} different benchmarks, together these
rank {\color{black}\numTools~} distinct software packages.

@@

\section*{Data availability}
Raw datasets, software and documents are available under a CC-BY license:\\
%\fussy
%\url{https://docs.google.com/spreadsheets/d/14xIY2PHNvxmV9MQLpbzSfFkuy1RlzDHbBOCZLJKcGu8/edit?usp=sharing}\\
%and here:\\
%\fussy
%\url{https://dx.doi.org/10.6084/m9.figshare.4299320.v1}\\
%\sloppy
%Additional documentation, code, figures and raw data is available here:\\
\fussy
\url{https://github.com/Gardner-BinfLab/speed-vs-accuracy-meta-analysis}
\sloppy

@@

%{\bf AND ETC....}
